% Appendix B

\chapter{Data extraction form for literature review}
\label{appendixb}
\lhead{Appendix B. \emph{Data extraction form for literature review}}

\textbf{General information}

\begin{itemize}
\item Date of extraction

\item Study identification

\begin{itemize}
\item Unique reference number

\item Author

\item Title

\item Source

\item First author affiliation and contact details

\item First author declared conflicts of interest

\end{itemize}

\item Reviewer identification

\item Notes

\end{itemize}

\textbf{Specific information}

\begin{itemize}
\item Study eligibility

\begin{itemize}
\item Primary outcome

\item Intervention

\item Comparison

\item Study design

\end{itemize}

\item Population

\begin{itemize}
\item Population description

\begin{itemize}
\item Study setting e.g. Hospital\slash EMS UK\slash US\slash Canada Urban\slash Rural

\item Population served

\item No. of ALS ambulances (i.e. with paramedic)

\item No. of receiving hospitals (in study)

\end{itemize}

\item Inclusion criteria

\item Exclusion criteria

\item Recruitment procedure

\item Patient characteristics

\item Participants (i.e. paramedics\slash doctors\slash AHPs)

\begin{itemize}
\item Skill level

\item Length of service

\item No. of participants

\item Intervention\slash Control groups comparable?

\item Sample size calculation

\end{itemize}

\end{itemize}

\item Methodological quality of study

\begin{itemize}
\item Intervention

\begin{itemize}
\item Focus

\item Training provided prior to intervention

\item Duration of intervention

\item Delivery mode of intervention

\item Computer interpretation algorithm type

\end{itemize}

\item Ethics

\begin{itemize}
\item Appropriate approval obtained?

\end{itemize}

\end{itemize}

\item Outcomes and outcome measures

\begin{itemize}
\item What was measured at baseline?

\item What was measured after the intervention?

\item Used of validated tools (and if so, how)?

\item Time intervals between first and second measurements

\item Time interval between first and last measurements

\item Adverse events

\end{itemize}

\item Analysis

\begin{itemize}
\item Statistical techniques used

\item Adjustment for confounding or clustering?

\item Attrition rates

\item How was attrition managed?

\item Number followed up

\item Number lost to follow up

\item Reasons for participants lost to follow up

\end{itemize}

\item Results

\begin{itemize}
\item Quantitative results

\item Qualitative results (if applicable)

\item Cost of intervention

\item Cost effectiveness

\item Conclusion

\item Funding source

\end{itemize}

\item Notes

\end{itemize}
