---
title: "RESPECT Feasibility Study - Analysis script"
author: "Richard Pilbery"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

RESPECT Analysis script
========================================================

Before you run this RMarkdown script, you need to have processed the data using the RawDataProcess.Rmd file, as this scripts starts by loading in data.frames that have been prepared.  In addition, you also need to specify a couple of file locations:

+ Path to winBUGS-correct directory
+ Path to winBUGS-incorrect directory

```{r loadInData}
 load("FSD4knitr99.Rdata")
 load("FSD4knitr.Rdata")
 load("UP994knitr.Rdata")

pathToWinbugsIncorrect <- '/Users/tricky999/Dropbox/RData/winBUGS-incorrect/'
lockBinding("pathToWinbugsIncorrect", globalenv())
pathToWinbugsCorrect <- '/Users/tricky999/Dropbox/RData/winBUGS-correct/'
lockBinding("pathToWinbugsCorrect", globalenv())

```
Load in the files containing the dataframes, FinalStudyData99 and ParticipantData
Convert the classification column values to a factor (think categorical data)
```{r}
 FinalStudyData99$classification <- factor(FinalStudyData99$classification)
```
Create two subsets of the data, FSD99CC containing data where the computer was correct (i.e. true positives and true negatives) and FSD99CI, which contains data where the computer was incorrect.

```{r}
FSD99CC <- subset(FinalStudyData99,FinalStudyData99$truepos==1|FinalStudyData99$trueneg==1)
FSD99CI <- subset(FinalStudyData99,FinalStudyData99$falsepos==1|FinalStudyData99$falseneg==1)
```

Create two subsets of the unpaired data, UPFSD99CC containing data where the computer was correct (i.e. true positives and true negatives) and UPFSD99CI, which contains data where the computer was incorrect.

```{r}
UPFSD99CC <- subset(unpairedFinalData99,unpairedFinalData99$truepos==1|unpairedFinalData99$trueneg==1)
UPFSD99CI <- subset(unpairedFinalData99,unpairedFinalData99$falsepos==1|unpairedFinalData99$falseneg==1)
```


In order to maximise reproducability, these scripts use the checkpoint package.  This needs loading:

```{r results='hide',message=FALSE,warning=FALSE}
library(checkpoint)
checkpoint('2015-04-12')
```

The rest of the analysis requires a number of R packages including:
```{r results='hide',message=FALSE,warning=FALSE}
require('epitools')
require('xtable')
```
Odds Ratio Table
------------
makeBasicORTable is a function that returns the OR table.  By default it will calculate an OR table for all data, unless the variable ORtableName is set to FSD99CC or FSD99CI.  The Odds ratios for the unpaired data are also calculated in order to provide a comparison for the results that were excluded from the analysis.
```{r OddsRatioTableFunction, results='hide'}
 makeBasicORTable <- function(ORtableName='') {
   # NULL is FinalStudyData99 i.e. all data pairs
   # FSD99CC - only includes data with correct computer interpretation
   # FSD99CI - only includes data with incorrect computer interpretation
   if(ORtableName=='FSD99CC') FSD = FSD99CC
   else if(ORtableName=='FSD99CI') FSD = FSD99CI
   else if(ORtableName=='UFD99') FSD = unpairedFinalData99
   else if(ORtableName=='UFD99CC') FSD = UPFSD99CC
   else if(ORtableName=='UFD99CI') FSD = UPFSD99CI
   else FSD = FinalStudyData99
   ORT <- epitools::oddsratio(FSD$message_visible,FSD$diag_correct,verbose=T)
   #print(ORT) 
   
 } 
 
 ORtableAll <- makeBasicORTable()
 ORtableCC <- makeBasicORTable("FSD99CC")
 ORtableCI <- makeBasicORTable("FSD99CI")
 ORunpairedtable <- makeBasicORTable("UFD99")
 ORunpairedtableCC <- makeBasicORTable("UFD99CC")
 ORunpairedtableCI <- makeBasicORTable("UFD99CI")
```
The resulting tables (note that the predictor is the computer message visibility, 0 for hidden, 1 for visible and outcome is the participant interpretation being correct (1) or incorrect (0):

### Odds ratio table for all results
```{r oddsRatioForAllResults, echo=FALSE}
ORtable <- ORtableAll
```

|             ||      Participant interpretation       ||
|-------------|:--------:|:-------------------:|:------:|
| **Message**     |Correct   | Incorrect           |Total   |
| Visible     |`r ORtable$data[5]` (`r round((ORtable$data[5]/ORtable$data[8])*100)`%) |`r ORtable$data[2]` (`r round((ORtable$data[2]/ORtable$data[8])*100)`%) |`r ORtable$data[8] `  |
| Hidden      |`r ORtable$data[4]` (`r round((ORtable$data[4]/ORtable$data[7])*100)`%)| `r ORtable$data[1]` (`r round((ORtable$data[1]/ORtable$data[7])*100)`%) | `r ORtable$data[7] `  |
| Total       | `r ORtable$data[6]` (`r round((ORtable$data[6]/ORtable$data[9])*100)`%) |`r ORtable$data[3]` (`r round((ORtable$data[3]/ORtable$data[9])*100)`%)  | `r ORtable$data[9] ` |


### Odds ratio table for correct computer interpretations
```{r echo=FALSE}
ORtable <- ORtableCC
```

|             ||      Participant interpretation       ||
|-------------|:--------:|:-------------------:|:------:|
| **Message**     |Correct   | Incorrect           |Total   |
| Visible     |`r ORtable$data[5]` (`r round((ORtable$data[5]/ORtable$data[8])*100)`%) |`r ORtable$data[2]` (`r round((ORtable$data[2]/ORtable$data[8])*100)`%) |`r ORtable$data[8] `  |
| Hidden      |`r ORtable$data[4]` (`r round((ORtable$data[4]/ORtable$data[7])*100)`%)| `r ORtable$data[1]` (`r round((ORtable$data[1]/ORtable$data[7])*100)`%) | `r ORtable$data[7] `  |
| Total       | `r ORtable$data[6]` (`r round((ORtable$data[6]/ORtable$data[9])*100)`%) |`r ORtable$data[3]` (`r round((ORtable$data[3]/ORtable$data[9])*100)`%)  | `r ORtable$data[9] ` |

###  Odds ratio table for incorrect computer interpretations
```{r echo=FALSE}
ORtable <- ORtableCI
```

|             ||      Participant interpretation       ||
|-------------|:--------:|:-------------------:|:------:|
| **Message**     |Correct   | Incorrect           |Total   |
| Visible     |`r ORtable$data[5]` (`r round((ORtable$data[5]/ORtable$data[8])*100)`%) |`r ORtable$data[2]` (`r round((ORtable$data[2]/ORtable$data[8])*100)`%) |`r ORtable$data[8] `  |
| Hidden      |`r ORtable$data[4]` (`r round((ORtable$data[4]/ORtable$data[7])*100)`%)| `r ORtable$data[1]` (`r round((ORtable$data[1]/ORtable$data[7])*100)`%) | `r ORtable$data[7] `  |
| Total       | `r ORtable$data[6]` (`r round((ORtable$data[6]/ORtable$data[9])*100)`%) |`r ORtable$data[3]` (`r round((ORtable$data[3]/ORtable$data[9])*100)`%)  | `r ORtable$data[9] ` |

### Odds ratio table for all unpaired results
```{r echo=FALSE}
ORtable <- ORunpairedtable
```

|             ||      Participant interpretation       ||
|-------------|:--------:|:-------------------:|:------:|
| **Message**     |Correct   | Incorrect           |Total   |
| Visible     |`r ORtable$data[5]` (`r round((ORtable$data[5]/ORtable$data[8])*100)`%) |`r ORtable$data[2]` (`r round((ORtable$data[2]/ORtable$data[8])*100)`%) |`r ORtable$data[8] `  |
| Hidden      |`r ORtable$data[4]` (`r round((ORtable$data[4]/ORtable$data[7])*100)`%)| `r ORtable$data[1]` (`r round((ORtable$data[1]/ORtable$data[7])*100)`%) | `r ORtable$data[7] `  |
| Total       | `r ORtable$data[6]` (`r round((ORtable$data[6]/ORtable$data[9])*100)`%) |`r ORtable$data[3]` (`r round((ORtable$data[3]/ORtable$data[9])*100)`%)  | `r ORtable$data[9] ` |

###  Odds ratio table for all correct computer interpretation unpaired results
```{r echo=FALSE}
ORtable <- ORunpairedtableCC
```

|             ||      Participant interpretation       ||
|-------------|:--------:|:-------------------:|:------:|
| **Message**     |Correct   | Incorrect           |Total   |
| Visible     |`r ORtable$data[5]` (`r round((ORtable$data[5]/ORtable$data[8])*100)`%) |`r ORtable$data[2]` (`r round((ORtable$data[2]/ORtable$data[8])*100)`%) |`r ORtable$data[8] `  |
| Hidden      |`r ORtable$data[4]` (`r round((ORtable$data[4]/ORtable$data[7])*100)`%)| `r ORtable$data[1]` (`r round((ORtable$data[1]/ORtable$data[7])*100)`%) | `r ORtable$data[7] `  |
| Total       | `r ORtable$data[6]` (`r round((ORtable$data[6]/ORtable$data[9])*100)`%) |`r ORtable$data[3]` (`r round((ORtable$data[3]/ORtable$data[9])*100)`%)  | `r ORtable$data[9] ` |

###  Odds ratio table for all incorrect computer interpretation unpaired results
```{r echo=FALSE}
ORtable <- ORunpairedtableCI
```

|             ||      Participant interpretation       ||
|-------------|:--------:|:-------------------:|:------:|
| **Message**     |Correct   | Incorrect           |Total   |
| Visible     |`r ORtable$data[5]` (`r round((ORtable$data[5]/ORtable$data[8])*100)`%) |`r ORtable$data[2]` (`r round((ORtable$data[2]/ORtable$data[8])*100)`%) |`r ORtable$data[8] `  |
| Hidden      |`r ORtable$data[4]` (`r round((ORtable$data[4]/ORtable$data[7])*100)`%)| `r ORtable$data[1]` (`r round((ORtable$data[1]/ORtable$data[7])*100)`%) | `r ORtable$data[7] `  |
| Total       | `r ORtable$data[6]` (`r round((ORtable$data[6]/ORtable$data[9])*100)`%) |`r ORtable$data[3]` (`r round((ORtable$data[3]/ORtable$data[9])*100)`%)  | `r ORtable$data[9] ` |



Crossover Table
-------------------
It was pointed out to me that the simple 2x2 tables output above do not show the crossover.  So, the data below will address that.

This requires the R package plyr()
```{r results='hide',message=FALSE,warning=FALSE}
require('plyr')
```

Prepare the data to collate the frequences:
```{r crossOverTables, results='hide' }

crossoverDataPrep <- function(dataTableName='') {
  if(dataTableName=='FSD99CC') FSD = FSD99CC
  else if(dataTableName=='FSD99CI') FSD = FSD99CI
  else FSD = FinalStudyData99
  sortData <- ddply(FSD,c("participant_id","ecg_id","message_visible"),transform)
  crossoverData <- ddply(sortData,c("participant_id","ecg_id"),function(x)ifelse(x$diag_correct[1] == 1 & x$diag_correct[2] == 1,"CC",ifelse(x$diag_correct[1] == 0 & x$diag_correct[2] == 0,"II",ifelse(x$diag_correct[1] == 1 & x$diag_correct[2] == 0,"CI","IC"))))
  sumXOver <- count(crossoverData,c("V1"))
  print(sumXOver)
}

sumXOverAll <- crossoverDataPrep()
sumXOverCC <- crossoverDataPrep('FSD99CC')
sumXOverCI <- crossoverDataPrep('FSD99CI')

```

#### Here is the 2x2 Crossover table for all results:

|             |           | Message Hidden                           ||                                           |
|-------------|:---------:|:--------------------:|:--------------------:|:-----------------------------------------:|
|             |           |  Correct             | Incorrect            | Total                                     |
| **Message** |  Correct  | `r sumXOverAll$freq[1]` | `r sumXOverAll$freq[3]` | `r sum(sumXOverAll$freq[1],sumXOverAll$freq[3])`|
| **Visible**  | Incorrect | `r sumXOverAll$freq[2]` | `r sumXOverAll$freq[4]` | `r sum(sumXOverAll$freq[2],sumXOverAll$freq[4])`|
|             | Total     | `r sum(sumXOverAll$freq[1],sumXOverAll$freq[2])` | `r sum(sumXOverAll$freq[3],sumXOverAll$freq[4])` | `r sum(sumXOverAll$freq[1],sumXOverAll$freq[2],sumXOverAll$freq[3],sumXOverAll$freq[4])`|

The Odds Ratio is `r sumXOverAll$freq[3]`/`r sumXOverAll$freq[2]` = `r sumXOverAll$freq[3]/sumXOverAll$freq[2]` 


#### Here is the 2x2 Crossover table for all correct computer interpretations

|             |           | Message Hidden                            ||                                           |
|-------------|:---------:|:--------------------:|:--------------------:|:-----------------------------------------:|
|             |           |  Correct             | Incorrect            | Total                                     |
| **Message** |  Correct  | `r sumXOverCC$freq[1]` | `r sumXOverCC$freq[3]` | `r sum(sumXOverCC$freq[1],sumXOverCC$freq[3])`|
| **Visible**  | Incorrect | `r sumXOverCC$freq[2]` | `r sumXOverCC$freq[4]` | `r sum(sumXOverCC$freq[2],sumXOverCC$freq[4])`|
|             | Total     | `r sum(sumXOverCC$freq[1],sumXOverCC$freq[2])` | `r sum(sumXOverCC$freq[3],sumXOverCC$freq[4])` | `r sum(sumXOverCC$freq[1],sumXOverCC$freq[2],sumXOverCC$freq[3],sumXOverCC$freq[4])`|

The Odds Ratio is `r sumXOverCC$freq[3]`/`r sumXOverCC$freq[2]` = `r sumXOverCC$freq[3]/sumXOverCC$freq[2]` 


#### Here is the 2x2 Crossover table for all incorrect computer interpretations:

|             |           | Message Hidden                           ||                                           |
|-------------|:---------:|:--------------------:|:--------------------:|:-----------------------------------------:|
|             |           |  Correct             | Incorrect            | Total                                     |
| **Message** |  Correct  | `r sumXOverCI$freq[1]` | `r sumXOverCI$freq[3]` | `r sum(sumXOverCI$freq[1],sumXOverCI$freq[3])`|
| **Visible**  | Incorrect | `r sumXOverCI$freq[2]` | `r sumXOverCI$freq[4]` | `r sum(sumXOverCI$freq[2],sumXOverCI$freq[4])`|
|             | Total     | `r sum(sumXOverCI$freq[1],sumXOverCI$freq[2])` | `r sum(sumXOverCI$freq[3],sumXOverCI$freq[4])` | `r sum(sumXOverCI$freq[1],sumXOverCI$freq[2],sumXOverCI$freq[3],sumXOverCI$freq[4])`|

The Odds Ratio is `r sumXOverCI$freq[3]`/`r sumXOverCI$freq[2]` = `r sumXOverCI$freq[3]/sumXOverCI$freq[2]` 


Conditional Logistic Regression
------------
First, straight conditional logistic regression without random effects, using the clogit() function in the survival package.

```{r results='hide',message=FALSE,warning=FALSE}
require('survival') || install.packages('survival')
require('mclogit')
```

```{r clogitAnalysis}
clogitAnalysis <- function(ORtableName='',typeOfClogit=''){
  if(ORtableName=='FSD99CC') FSD = FSD99CC
  else if(ORtableName=='FSD99CI') FSD = FSD99CI
  else FSD = FinalStudyData99
  if(typeOfClogit=='mclogit') typeClog = 'mclogit'
  else typeClog = 'clogit'
  clogPrepData <- subset(FSD,select=c("quiz_id","participant_id","ecg_id","diag_correct","message_visible"))
  rowNumbers = nrow(clogPrepData)/2
  clogPrepData$stratum <- rep(1:rowNumbers,each=2)
  
  if(typeClog=='clogit') {
    clogAll <- clogit(message_visible~diag_correct+strata(stratum),data=clogPrepData)

    print(summary(clogAll))
  }

}
```

All results:
```{r clogitAnalysisAllResults } 
  clogitAnalysis() 
```

Computer Correct interpretations:
```{r clogitAnalysisCC } 
  clogitAnalysis('FSD99CC') 
```

Computer Incorrect interpretations:
```{r clogitAnalysisCI } 
  clogitAnalysis('FSD99CI') 
```


Sensitivity and Specificity
---------------
This requires the R package, epiR()
```{r results='hide',message=FALSE,warning=FALSE}
library(epiR)
```
The first step is to create the function to create the tables from which the sensitvity and specificity can be calculated
```{r sensitivityAndSpecificity }
makeSStable <- function(SSdf,message) {
  #Create table to calculate sensitivity and sepcificity stats
  sPosaPos <- SSdf$freq[SSdf$answer==1&SSdf$stemi==1&SSdf$message_visible==message]
  sPosaNeg <- SSdf$freq[SSdf$answer==1&SSdf$stemi==0&SSdf$message_visible==message]
  sNegaPos <- SSdf$freq[SSdf$answer==0&SSdf$stemi==1&SSdf$message_visible==message]
  sNegaNeg <- SSdf$freq[SSdf$answer==0&SSdf$stemi==0&SSdf$message_visible==message]
  
  dat <- as.table(matrix(c(sPosaPos,sPosaNeg,sNegaPos,sNegaNeg), nrow = 2, byrow = TRUE))
  colnames(dat) <- c("STEMI+","STEMI-")
  rownames(dat) <- c("PARA+","PARA-")
  if(message) {
    cat("Message Visible\n")
  }
  else cat("Message Hidden\n")
  print(dat)
  # Calculate results of tests using epi.tests
  # Verbose = T important if you want to capture the output in a variabl
  epiSS <- epi.tests(dat, conf.level = 0.95)
  return(epiSS)
}
  # Get results for message visible and hidden for all responses.
  SSdf <- count(FinalStudyData99,c("answer","stemi","message_visible"))
  mesgVisAll <- makeSStable(SSdf,1)
  mesgHideAll <- makeSStable(SSdf,0)
  #print(mesgVisAll)

SStable <- NULL
# Create table to hold data and add All computer interpretation results
SStable <- rbind(c("All",round(mesgVisAll$elements$se*100),round(mesgVisAll$elements$sp*100),round(mesgHideAll$elements$se*100),round(mesgHideAll$elements$sp*100)))

# Correct computer interpretations
SSdfCC <- count(subset(FinalStudyData99,FinalStudyData99$computer_diagnosis==FinalStudyData99$stemi),c("answer","stemi","message_visible"))
mesgVisCC <- makeSStable(SSdfCC,1)
mesgHideCC <- makeSStable(SSdfCC,0)
SStable <- rbind(SStable,c("Correct",round(mesgVisCC$elements$se*100),round(mesgVisCC$elements$sp*100),round(mesgHideCC$elements$se*100),round(mesgHideCC$elements$sp*100)))

# Incorrect computer interpretations
SSdfCI <- count(subset(FinalStudyData99,FinalStudyData99$computer_diagnosis!=FinalStudyData99$stemi),c("answer","stemi","message_visible"))

mesgVisCI <- makeSStable(SSdfCI,1)
mesgHideCI <- makeSStable(SSdfCI,0)

SStable <- rbind(SStable,c("Incorrect",round(mesgVisCI$elements$se*100),round(mesgVisCI$elements$sp*100),round(mesgHideCI$elements$se*100),round(mesgHideCI$elements$sp*100)))

SStable <- as.data.frame(SStable)
colnames(SStable) <- c("Computer interpretation","Sensitivity","Specificity","Sensitivity","Specificity")

```
The results are created as Latex tables, using the xtable() package as they were then inserted directly into my dissertation.  I've hidden the actual latex code which is generated, but the final table output is this:
```{r results='hide',message=FALSE,warning=FALSE, echo=FALSE}
require('xtable')

xtableSS<-xtable(SStable,caption="Summary table of Sensitivities and Specificities of participant responses",label="partsensspec",digits=0)

finalxtableSS<- print.xtable(xtableSS,append=F,table.placement="htbp",caption.placement="top",booktabs=TRUE,include.rownames=FALSE)
finalxtableSSub <- sub("\\begin{tabular}{lllll}",
                        "\\newcolumntype{D}{>{\\arraybackslash}p{0.3\\textwidth}}
                        \\newcolumntype{E}{>{\\centering\\arraybackslash}p{0.12\\textwidth}}
                        \\newcolumntype{F}{>{\\centering\\arraybackslash}p{0.24\\textwidth}}
                        \\begin{tabular}{DEE|EE}
                       & \\multicolumn{2}{F}{Message Visible} & \\multicolumn{2}{F}{Message Hidden} \\\\",finalxtableSS,fixed=T)
cat(finalxtableSSub,file="Tables/partsensandspec.tex")
```
Note that the first 2 columns labelled Sensitivity and Specificity relate to the computer message being visible, and the last 2, when the message was hidden.
```{r}
print(SStable)
```

Conditional Logistic Regression with Random Effects
--------------------

In order to take account of clustering, a random effects or multi-level model was used.  In fact it is a cross-classified model as both the ECG and participant are a cluster on any ECG interpretation attempt.  To do this in R, I tried to use both the lme4 and coxme packages.

Neither worked, so in the end, Dawn Teare at the School of Health and Related Research, University of Sheffield, provided a model to undertake a Bayesian analysis using the package WinBUGS. I was able to use this inside R, thanks to the R2WinBUGS() package and installing the [WinBUGS package](http://www.mrc-bsu.cam.ac.uk/software/bugs/the-bugs-project-winbugs/) on my mac and using WINE to acutally run it.

Note that the bugs() instructions are blanked out. You may need to change the WINE and WINEPATH strings to match the filepath to the respective files.
````{r WinBUGS, width=60, results='hide',message=F,warning=F}

library('plyr')
library('R2WinBUGS')
library('coda')
library('tools')

processData <- function(df) {
  seq_participant_id <- data.frame(sort(unique(df$participant_id)))
  seq_participant_id[,2] <- seq(1,length(sort(unique(df$participant_id))))
  colnames(seq_participant_id) <- c('orig_id','new_id')
  
  seq_ecg_id <- data.frame(sort(unique(df$ecg_id)))
  seq_ecg_id[,2] <- seq(1,length(sort(unique(df$ecg_id))))
  colnames(seq_ecg_id) <- c('orig_id','new_id')
  
  newdata <- ddply(df,c("participant_id","ecg_id"),function(x)c(seq_participant_id$new_id[x$participant_id==seq_participant_id$orig_id],seq_ecg_id$new_id[x$ecg_id==seq_ecg_id$orig_id],x$diagnomessage,x$diagmessage))
  colnames(newdata) <- c('orig_participant_id','orig_ecg_id','participant_id','ecg_id','diagnomessage','diagmessage')
  
return(newdata)
}

processData2 <- function(df) {
  newdata <- ddply(df,c("participant_id","ecg_id"),function(x)
    {
      c(x$diag_correct[1],x$diag_correct[2])
    }
  )
  colnames(newdata) <- c('participant_id','ecg_id','diagnomessage','diagmessage')
  newdata <- subset(newdata,diagnomessage!=diagmessage)
  
  return(newdata)
}

newCC <- processData2(FSD99CC)
newCI <- processData2(FSD99CI)

newCC <- processData(newCC)
newCI <- processData(newCI)

````

R2WinBUGS has problems writing the data properly when processing matrices. Fortunately, Howard Seltman has provided code to handle this. The following functions are pretty much untouched from his originals: [BugsWrite.R script](http://www.stat.cmu.edu/~hseltman/files/BugsWrite.R), but I have customised a couple of functions for this analysis.

````{r BugListCode, width=60, results='hide',message=F,warning=F}

# Main function: Variable argument Bugs list writer.  See example above.
# Optional argument "columns=" is for writing dataframes or lists of dataframes
# and is handled specially; see example above and BugsWriteDataFrames().
# (Note: can't use "a=" due to a Bugs error!!)

BugsListWrite=function(file, append=FALSE, ...) {
  lst=list(...)
  nams=names(lst)
  columns=NULL  # for subselection of dataframe columns (assumes only 1 dtf)
  skip=0        # to skip "columns" when writing data
  nodim=FALSE   # use "nodim=TRUE" for older style Bugs format
  Sel=(nams=="columns" | nams=="nodim")
  if (any(Sel)) {
    SelColumn=(nams=="columns")
    if (any(SelColumn)) {
      SelColumn=(1:length(lst))[SelColumn]
    } else {
      SelColumn=0
    }
    SelNoDim=(nams=="nodim")
    if (any(SelNoDim)) {
      SelNoDim=(1:length(lst))[SelNoDim]
    } else {
      SelNoDim=0
    }
    if (SelColumn>0) {
      columns=unlist(lst[SelColumn])
      if (SelColumn==length(lst) || (SelNoDim==length(lst) && SelColumn==length(lst)-1)) {
        skip=SelColumn
      }
    }
    if (SelNoDim>0) {
      nodim=unlist(lst[SelNoDim])
      if (SelNoDim==length(lst) || (SelColumn==length(lst) && SelNoDim==length(lst)-1)) {
        skip=c(skip,SelNoDim)
      }
    }
  }
  N=length(lst)
  if (any(Sel) && any(skip>0)) N=N-sum(skip>0)
  if (is.null(nams) || any(unlist(lapply(lst,is.list))==FALSE & nams==""))
    stop("BugsListWrite requires named arguments")
  final=","
  for (i in 1:N) {
    if (any(skip==i)) continue
    if (i==N) final=")"
    if (i==1 || (i==2 && any(skip==1)) || (i==3 && any(skip==1) && any(skip==2))) {
      initial="list("
    } else {
      initial=""
    }
    if (!is.list(lst[[i]])) {
      initial=paste(initial, nams[i], "=", sep="")
    }
    dm=dim(lst[[i]])
    if (is.null(dm)) {
      if (is.list(lst[[i]])) {
        BugsDataFramesWrite(lst[[i]], file, columns, append, initial, final)
      } else {
        BugsVecWrite(lst[[i]], file, append, initial, final)
      }
    } else if (is.data.frame(lst[[i]])) {
      BugsDataFramesWrite(lst[[i]], file, columns, append, initial, final)
    } else if (length(dm)==2) {
      BugsMatWrite(lst[[i]], file, append, initial, final, nodim)
    } else if (length(dm)==3) {
      BugsArrayWrite(lst[[i]], file, append, initial, final, nodim)
    } else {
      warning(paste("BugsListWrite is skipping",nams[i]))
    }
    append=TRUE
  }
  invisible(NULL)
}

# Write a vector, by default as "myvec=c(mydata)"
BugsVecWrite=function(vec, file, append=TRUE, initial="", final="", perline=10) {
  if (initial=="") {
    initial=paste(deparse(substitute(vec)), "=", sep="")
  }
  if (length(vec)>1) initial=paste(initial, "c(", sep="")
  if (final=="") {
    if (length(vec)>1) final=")"
  } else {
    final=paste(ifelse(length(vec)>1,")",""), final, sep="")
  }
  BugsVecCoreWrite(vec, file, append, initial, final, perline)
  invisible(NULL)
}

# Write a matrix, by default as "myvec=structure(.Data=c(mydata),.Dim=c(rows,col))"
#  with transposition to acommodated Bugs convention of "first index moves slowest"
BugsMatWrite=function(mat, file, append=TRUE, initial="", final="", nodim=FALSE) {
  dm=dim(mat)
  if (is.null(dm) || length(dm)!=2) stop("BugsMatWrite needs a 2 dimensional matrix")
  
  if (initial=="") {
    initial=paste(deparse(substitute(mat)), "=", sep="")
  }
  perline=min(dm[2],10)
  if (nodim==FALSE) {
    initial=paste(initial, "structure(.Data=", sep="")
    BugsVecWrite(as.vector(t(mat)), file, append, initial, ",", perline)
    BugsVecWrite(dm, file, TRUE, ".Dim=", paste(")",final,sep=""))
  } else {
    BugsVecWrite(as.vector(t(mat)), file, append, initial, final, perline)
  }
  invisible(NULL)
}

# Write an array where the third (R) element is the matrix number
BugsArrayWrite=function(arr, file, append=TRUE, initial="", final="", nodim=FALSE) {
  if (!is.array(arr)) stop("BugsArrayWrite requires and array argument")
  if (is.matrix(arr)) {
    BugsMatWrite(arr, file, append, initial, final)
    return(invisible(NULL))
  }
  dm=dim(arr)
  if (length(dm)!=3) stop("BugsArrayWrite only handles 3 dimensional arrays for now")
  if (initial=="") initial=paste(deparse(substitute(arr)), "=", sep="")
  if (nodim==FALSE) {
    initial=paste(initial, "structure(.Data=c(", sep="")
  } else {
    initial=paste(initial, "c(", sep="")
  }
  stp=","
  for (i in 1:dm[3]) {
    if (i==dm[3]) {
      if (nodim==FALSE) {
        stp=paste("), .Dim=c(", paste(dm,collapse=","), "))", final, sep="")
      } else {
        stp=paste(")", final, sep="")
      }
    }
    BugsVecCoreWrite(as.vector(t(arr[,,i])), file, append, initial, stp)
    initial=""
    append=TRUE
  }
  invisible(NULL)
}

# Low level function: Write the core of a vector in bugs format, i.e. comma spaced numbers
# 10 per line with no final comma.
BugsVecCoreWrite=function(x, file, append=FALSE, initial="", final="", perline=10) {
  a=length(x)
  b=a%/%perline
  rem=a-perline*b
  if (b>0) {
    for (i in 1:b) {
      stp=i*perline
      strt=stp-perline+1
      w=paste(x[strt:stp],collapse=", ")
      if (i==1 && initial!="") w=paste(initial,w,sep="")
      if (i<b || rem>0)  {
        w=paste(w,",",sep="")
      } else {
        w=paste(w,final,sep="")
      }
      write(w, file=file, ncol=1, append=append)
      append=TRUE
    }
  }
  if (rem>0) {
    w=paste(x[(b*perline+1):a],collapse=", ")
    if (b==0) {
      w=paste(initial, w, sep="")
    }
    if (final!="") {
      w=paste(w,final,sep="")
    }
    write(w, file=file, ncol=1, append=append)
  }
  invisible(NULL)
}

````

A couple of customisations to make things work properly. The WriteList() function creates the files necessary for the WinBUGS analysis. You just need to add the model.

````{r BugslistCustomCode, width=60, results='hide',message=F,warning=F}
modbugs.data <- function (data, dir = getwd(), digits = 5, data.file = "data.txt") 
{
  if (is.numeric(unlist(data))) 
    if (is.R()) {
      R2WinBUGS:::write.datafile(lapply(data, formatC, digits = digits, 
                            format = "s"), file.path(dir, data.file))
    }
  else {
    if (is.R()) {
      data.list <- lapply(as.list(data), get, pos = parent.frame(2))
      names(data.list) <- as.list(data)
      R2WinBUGS:::write.datafile(lapply(data.list, formatC, digits = digits, 
                            format = "s"), file.path(dir, data.file))
    }
  }
  return(data.file)
}

writeList <- function(df,nameDF) {
  seq_df <- seq(1,nrow(df))
  outputDF <- data.frame(seq_df)
  outputDF[,2] <- 1
  outputDF[,3] <- as.integer(0)
  outputDF[,4] <- df$participant_id
  outputDF[,5] <- df$ecg_id
  outputDF[,6] <- df$diagmessage
  outputDF[,7] <- df$diagnomessage
  colnames(outputDF) <- c("row-id","con1","con0","participant","ecg","diag-message","diag-no-message")
  
  N <- nrow(outputDF)
  S <- length(unique(outputDF$participant))
  E <- length(unique(outputDF$ecg))
  t <- outputDF
  at <<- as.vector(t(outputDF))
  initialText <<- paste("list(N=",N,",S=",S,",E=",E,",t=",sep="")
  filename <- ""
  initsname <- ""
  if(nameDF=="FSD99CC") {
    filename <- paste(pathToWinbugsCorrect,nameDF,".txt",sep="")
    initsname <- c('WinBUGS-correct/inits.txt')
  }
  else {
    filename <- paste(pathToWinbugsIncorrect,nameDF,".txt",sep="")
    initsname <- c('WinBUGS-incorrect/inits.txt')
  }
  ecg <- rep(0,E)
  subs <- rep(0,S) 
  BugsMatWrite(outputDF,filename,initial=initialText)
  modbugs.data(list(beta=0.5,sde=0.1,sds=0.2,ecg=ecg,sub=subs),data.file=initsname)


}

writeList(newCI,"FSD99CI")
writeList(newCC,"FSD99CC")

````

The two lines in the code below set up the model. This identifies the data source, the initial values files (three of them due to their being three chains), and other values such as the number of iterations, burn in etc.

````{r BUGScodeRun, width=60, results='hide',message=F,warning=F}

#bugsTestI <- bugs(data=c("FSD99CI.txt"), inits=c("inits.txt","inits.txt","inits.txt"), parameters.to.save=c("beta","ecg","sds","sde"), model.file = "model.txt",program=c("WinBUGS"),n.chains = 3,n.iter = 1000000,n.burnin=6000,n.thin=5,digits=5, useWINE=TRUE,bugs.directory = "/Users/tricky999/.wine/drive_c/Program Files/WinBUGS14", working.directory = "./winBUGS-incorrect", WINE="/opt/local/bin/wine",WINEPATH="/opt/local/bin/winepath",debug=F,DIC=T,codaPkg=TRUE)

#bugsTestC <- bugs(data=c("FSD99CC.txt"), inits=c("inits.txt","inits.txt","inits.txt"), parameters.to.save=c("beta","ecg","sds","sde"), model.file = "model.txt",program=c("WinBUGS"),n.chains = 3,n.iter = 1000000,n.burnin=6000,n.thin=5,digits=5, useWINE=TRUE,bugs.directory = "/Users/tricky999/.wine/drive_c/Program Files/WinBUGS14", working.directory = "./winBUGS-correct", WINE="/opt/local/bin/wine",WINEPATH="/opt/local/bin/winepath",debug=F,DIC=T,codaPkg=TRUE)

````

Once a simulation has been run, it is not necessary to undertake this again. Instead, it's possible to load the results in directly.  The generateOR function will load in the correct coda file and calculate the OR, CI and ICC values for ECG and Participants.

````{r process-WinBUGS-data, results='hide',message=F,warning=F}

generateOR <- function(chain,dir) {
  filename <- paste(dir,'coda',chain,'.txt',sep='')
  print(filename)
  testCoda <- read.bugs(filename)
  summarytestCoda <- summary(testCoda)
  
  
  # Calculate the ICC values for ECGs and participants
  iccECG = (summarytestCoda$statistics['sde',1]^2)/(summarytestCoda$statistics['sds',1]^2+summarytestCoda$statistics['sde',1]^2+(pi^2/3))
  
  iccParticipant = (summarytestCoda$statistics['sds',1]^2)/(summarytestCoda$statistics['sds',1]^2+summarytestCoda$statistics['sde',1]^2+(pi^2/3))
  
  result <- c(exp(summarytestCoda$statistics[1]),exp(summarytestCoda$quantiles[1,1]),exp(summarytestCoda$quantiles[1,5]),iccECG,iccParticipant)
  
  # Returns c(OR, 2.5 CI, 97.5 CI, ICC ECG, ICC Participant)
  return(result)
  
}

# Calculate values for each chain

chainoneI <- generateOR(1,pathToWinbugsIncorrect)
chaintwoI <- generateOR(2,pathToWinbugsIncorrect)
chainthreeI <- generateOR(3,pathToWinbugsIncorrect)

chainoneC <- generateOR(1,pathToWinbugsCorrect)
chaintwoC <- generateOR(2,pathToWinbugsCorrect)
chainthreeC <- generateOR(3,pathToWinbugsCorrect)


````
#### Incorrect Computer Interpretation: Results from 3 chains


| Value / Chain    |      Chain 1      |      Chain 2         |            Chain 3 | 
|------------------|:-----------------:|:--------------------:|:-------------------:|
| **OR**          |  `r chainoneI[1]`  | `r chaintwoI[1]`     | `r chainthreeI[1]`  | 
| **95% CI**      | `r chainoneI[2]`-`r chainoneI[3]` | `r chaintwoI[2]`-`r chaintwoI[3]`  | `r chainthreeI[2]`-`r chainthreeI[3]` |
|  **ICC ECG**        | `r chainoneI[4]`   | `r chaintwoI[4]`     |  `r chainthreeI[4]` |
| **ICC Participants** | `r chainoneI[5]` | `r chaintwoI[5]`      |  `r chainthreeI[5]` |

Taking the mean values for all three incorrect computer interpretation chains gives the following results:

+ OR: `r (chainoneI[1]+chaintwoI[1]+chainthreeI[1])/3`
+ 95%CI: `r (chainoneI[2]+chaintwoI[2]+chainthreeI[2])/3`-`r (chainoneI[3]+chaintwoI[3]+chainthreeI[3])/3`
+ ICC ECG: `r (chainoneI[4]+chaintwoI[4]+chainthreeI[4])/3`
+ ICC Participants: `r (chainoneI[5]+chaintwoI[5]+chainthreeI[5])/3`


#### Correct Computer Interpretation: Results from 3 chains


| Value / Chain    |      Chain 1      |      Chain 2         |            Chain 3 | 
|------------------|:-----------------:|:--------------------:|:-------------------:|
| **OR**          |  `r chainoneC[1]`  | `r chaintwoC[1]`     | `r chainthreeC[1]`  | 
| **95% CI**      | `r chainoneC[2]`-`r chainoneC[3]` | `r chaintwoI[2]`-`r chaintwoC[3]`  | `r chainthreeC[2]`-`r chainthreeC[3]` |
|  **ICC ECG**        | `r chainoneC[4]`   | `r chaintwoC[4]`     |  `r chainthreeC[4]` |
| **ICC Participants** | `r chainoneC[5]` | `r chaintwoC[5]`      |  `r chainthreeC[5]` |

Taking the mean values for all three correct computer interpretation chains gives the following results:

+ OR: `r (chainoneC[1]+chaintwoC[1]+chainthreeC[1])/3`
+ 95%CI: `r (chainoneC[2]+chaintwoC[2]+chainthreeC[2])/3`-`r (chainoneC[3]+chaintwoC[3]+chainthreeC[3])/3`
+ ICC ECG: `r (chainoneC[4]+chaintwoC[4]+chainthreeC[4])/3`
+ ICC Participants: `r (chainoneC[5]+chaintwoC[5]+chainthreeC[5])/3`
