---
title: "Carryover and Period Effect Calculations"
author: "Richard Pilbery"
date: "10 August 2015"
output: html_document
---

RESPECT Pilot Study - Assessing for Carryover and Period Effects
========================================================

This script loads in the processed data and runs tests for carryover and period effects.  It is based on a [presentation](http://nickfieller.staff.shef.ac.uk/tampere/clinicalslidesThursday.pdf) given by Dr Nick Feller.

In order to maximise reproducability, these scripts use the checkpoint package.  This needs loading:

```{r results='hide',message=FALSE,warning=FALSE}
library(checkpoint)
checkpoint('2015-08-10')
```

Load the required package, dplyr
```{r results='hide',message=FALSE,warning=FALSE}
library(dplyr)
```

Load in the data and prepare it:
```{r loadInData}
load("FSD4knitr99.Rdata")
FinalStudyData99$classification <- factor(FinalStudyData99$classification)
```
Create two subsets of the data, FSD99CC containing data where the computer was correct (i.e. true positives and true negatives) and FSD99CI, which contains data where the computer was incorrect.

```{r}
FSD99CC <- subset(FinalStudyData99,FinalStudyData99$truepos==1|FinalStudyData99$trueneg==1)
FSD99CI <- subset(FinalStudyData99,FinalStudyData99$falsepos==1|FinalStudyData99$falseneg==1)
```

Carryover Effects
------------------

The createDF function returns 

```{r createDF-function}

createDF <- function(dataframe=FinalStudyData99)  { 
    carryoverdf <- dataframe %>%
      select(qn_number, participant_id, ecg_id, message_visible, classification, 
             diag_correct) %>%
      mutate(attempt = ifelse(qn_number < 13, 'attempt1', 'attempt2')) %>%
      group_by(participant_id, ecg_id) %>%
        summarise(
          sequence = ifelse(attempt[1] == 'attempt1','hv','vh'),
          diag_correct1 = ifelse(attempt[1] == 'attempt1',diag_correct[1],diag_correct[2]),
          diag_correct2 = ifelse(attempt[1] == 'attempt2',diag_correct[1],diag_correct[2]) 
        ) %>%
      group_by(sequence) %>%
      summarise(
        correct1st = sum(diag_correct1),
        correct2nd = sum(diag_correct2)
      ) %>%
      arrange(desc(sequence))
}

```

Run the function for computer correct, computer incorrect and all interpretions:

````{r functionCalls, message=FALSE,warning=FALSE}

compcorrectDF <- createDF(FSD99CC)
compincorrectDF <- createDF(FSD99CI)
compallDF <- createDF()

```

### Summary tables for Carryover effect calculations
#### Computer correct interpretations

| Sequence          | Correct 1st attempt             |         Correct 2nd attempt     |
|:------------------|:-------------------------------:|:-------------------------------:|
| Visible -> Hidden | `r compcorrectDF$correct1st[1]` | `r compcorrectDF$correct2nd[1]` |
| Hidden -> Visible | `r compcorrectDF$correct1st[2]` | `r compcorrectDF$correct2nd[2]` |

#### Computer incorrect interpretations

| Sequence          | Correct 1st attempt             |         Correct 2nd attempt     |
|:------------------|:-------------------------------:|:-------------------------------:|
| Visible -> Hidden | `r compincorrectDF$correct1st[1]` | `r compincorrectDF$correct2nd[1]` |
| Hidden -> Visible | `r compincorrectDF$correct1st[2]` | `r compincorrectDF$correct2nd[2]` |

#### All interpretations

| Sequence          | Correct 1st attempt             |         Correct 2nd attempt     |
|:------------------|:-------------------------------:|:-------------------------------:|
| Visible -> Hidden | `r compallDF$correct1st[1]` | `r compallDF$correct2nd[1]` |
| Hidden -> Visible | `r compallDF$correct1st[2]` | `r compallDF$correct2nd[2]` |

The chithesquare function creates a matrix from the createDF function and then performs a Chi-squared test on the resulting 2x2 table

````{r chiSQ, width=60}
chithesquare <- function(df) {
    chisq.test(matrix(c(df$correct1st[1],df$correct1st[2],df$correct2nd[1],df$correct2nd[1]),
                      ncol=2,nrow=2))
  }
```

Run the chithesquare function on computer correct, computer incorrect and all results

````{r functionCalls2, message=FALSE,warning=FALSE}
csCeAll <- chithesquare(compallDF)
csCeCI <- chithesquare(compincorrectDF)
csCeCC <- chithesquare(compcorrectDF)
```


#### Summary of carryover tests

| Dataset            |      chi-squared            |      p-value         |
|--------------------|:---------------------------:|:--------------------:|
| All data           |  `r round(csCeAll$statistic[[1]],3)` | `r round(csCeAll$p.value,3)`  | 
| Computer correct   |  `r round(csCeCC$statistic[[1]],3)`  | `r round(csCeCC$p.value,3)`   |
| Computer incorrect |  `r round(csCeCI$statistic[[1]],3)`  | `r round(csCeCI$p.value,3)`   |

Period Effects
------------------

Next, we need to test for period effects.  This is achieved by summarising the data using the createPeriodDF function and running them through the chithesquare function.

```{r createPeriodDF-function}
createPeriodDF <- function(dataframe=FinalStudyData99)  { 
  carryoverdf <- dataframe %>%
    select(qn_number, participant_id, ecg_id, message_visible, 
           classification, diag_correct) %>%
    mutate(attempt = ifelse(qn_number < 13, 'attempt1', 'attempt2')) %>%
    group_by(participant_id, ecg_id) %>%
    summarise(
      sequence = ifelse(attempt[1] == 'attempt1','hv','vh'),
      corr_vis = ifelse(diag_correct[1], 0, 1),
      corr_hid = ifelse(diag_correct[1], 1, 0) 
    ) %>%
    group_by(sequence) %>%
    summarise(
      Vis = sum(corr_vis),
      Hid = sum(corr_hid)
    ) %>%
    arrange(desc(sequence))
} 
```

````{r functionCalls3}
compcorrectPDF <- createPeriodDF(FSD99CC)
compincorrectPDF <- createPeriodDF(FSD99CI)
compallPDF <- createPeriodDF()
```

### Summary tables for Period effect calculations
#### Computer correct interpretations

| Sequence          | Correct when message visible | Correct when message hidden |
|:------------------|:-------------------------:|:-------------------------:|
| Visible -> Hidden | `r compcorrectPDF$Vis[1]` | `r compcorrectPDF$Hid[1]` |
| Hidden -> Visible | `r compcorrectPDF$Vis[2]` | `r compcorrectPDF$Hid[2]` |

#### Computer incorrect interpretations

| Sequence          | Correct when message visible | Correct when message hidden |
|:------------------|:---------------------------:|:---------------------------:|
| Visible -> Hidden | `r compincorrectPDF$Vis[1]` | `r compincorrectPDF$Hid[1]` |
| Hidden -> Visible | `r compincorrectPDF$Vis[2]` | `r compincorrectPDF$Hid[2]` |

#### All interpretations

| Sequence          | Correct when message visible | Correct when message hidden |
|:------------------|:---------------------:|:---------------------:|
| Visible -> Hidden | `r compallPDF$Vis[1]` | `r compallPDF$Hid[1]` |
| Hidden -> Visible | `r compallPDF$Vis[2]` | `r compallPDF$Hid[2]` |


The chithePsquare function creates a matrix from the createPeriodDF function and then performs a Chi-squared test on the resulting 2x2 table

```{r chithePsquare, width=60}
chithePsquare <- function(df) {
  chisq.test(matrix(c(df$Vis[1],df$Vis[2],df$Hid[1],df$Hid[1]),
                    ncol=2,nrow=2))
}
```

```{r functionCalls4}
csPeAll <- chithePsquare(compallPDF)
csPeCI <- chithePsquare(compincorrectPDF)
csPeCC <- chithePsquare(compcorrectPDF)
```

### Summary of period tests

| Dataset            |      chi-squared            |      p-value         |
|--------------------|:---------------------------:|:--------------------:|
| All data           |  `r round(csPeAll$statistic[[1]],3)` | `r round(csPeAll$p.value,3)`  | 
| Computer correct   |  `r round(csPeCC$statistic[[1]],3)`  | `r round(csPeCC$p.value,3)`   |
| Computer incorrect |  `r round(csPeCI$statistic[[1]],3)`  | `r round(csPeCI$p.value,3)`   |

So, it looks like there is no significant carryover or period effects in this sample

